### 2009-04-17 docs/runtime_parameters/runtime_parameters.tex
-fixed outdated comments in advance.f90 -more progress on runtime_parameters.tex -added new flag to _parameters: p0_update_type, default 1  # How we update the base state pressure and compute psi. @@  # 1 = call {\tt advect\_base\_pres}; @@  # 2 = call {\tt enforce\_HSE}.

@@

\verb=  model_file  = &    &  "model.hse" \\

@@

@@

\verb=  plot_base  = &    &  .false. \\
\verb=  plot_base_name  = &    &  "plt" \\
\verb=  plot_deltat  = &    &  0.0 \\
\verb=  plot_int  = &    &  0 \\
\verb=  plot_spec  = &    &  .true. \\
\verb=  plot_trac  = &    &  .false. \\
\verb=  pmask_x  = &    &  .false. \\
\verb=  pmask_y  = &    &  .false. \\
\verb=  pmask_z  = &    &  .false. \\

@@

\verb=  prob_hi_x  = &    &  1.0 \\
\verb=  prob_hi_y  = &    &  1.0 \\
\verb=  prob_hi_z  = &    &  1.0 \\
\verb=  prob_lo_x  = &    &  ZERO \\
\verb=  prob_lo_y  = &    &  ZERO \\
\verb=  prob_lo_z  = &    &  ZERO \\

@@

\verb=  restart  = &    &  -1 \\

@@

\verb=  spherical_in  = &    &  0 \\
\verb=  sponge_kappa  = &    &  10.d0 \\
\verb=  stop_time  = &    &  -1.d0 \\

>>>>

\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  -1 \\

@@

\verb=  model_file  = &   input model file  &  "model.hse" \\

@@

\verb=  p0_update_type  = &   How we update the base state pressure and compute psi. \newline 1 = call {\tt advect\_base\_pres}; \newline 2 = call {\tt enforce\_HSE}.  &  1 \\

@@

\verb=  plot_base  = &   plot w0\_x, w0\_y, w0\_z, divw0, rho0, rhoh0, h0, and p0 in plotfile  &  .false. \\
\verb=  plot_base_name  = &   prefix to use in plotfile file names  &  "plt" \\
\verb=  plot_deltat  = &   rather than use a plot interva, plot a file after the solution has advanced past plot\_deltat in time  &  0.0 \\
\verb=  plot_int  = &   plot interval  &  0 \\
\verb=  plot_spec  = &   plot species and omegadot in plotfile  &  .true. \\
\verb=  plot_trac  = &   plot tracers in plotfile  &  .false. \\
\verb=  pmask_x  = &   indicates whether the problem domain periodic in the x-direction  &  .false. \\
\verb=  pmask_y  = &   indicates whether the problem domain periodic in the y-direction  &  .false. \\
\verb=  pmask_z  = &   indicates whether the problem domain periodic in the z-direction  &  .false. \\

@@

\verb=  prob_hi_x  = &   physical coordinates of hi-x corner of problem domain  &  1.0 \\
\verb=  prob_hi_y  = &   physical coordinates of hi-y corner of problem domain  &  1.0 \\
\verb=  prob_hi_z  = &   physical coordinates of hi-z corner of problem domain  &  1.0 \\
\verb=  prob_lo_x  = &   physical coordinates of lo-x corner of problem domain  &  ZERO \\
\verb=  prob_lo_y  = &   physical coordinates of lo-y corner of problem domain  &  ZERO \\
\verb=  prob_lo_z  = &   physical coordinates of lo-z corner of problem domain  &  ZERO \\

@@

\verb=  restart  = &   which file to restart from.  -1 means do not restart  &  -1 \\

@@

\verb=  spherical_in  = &   set to 1 if you are doing a spherical problem  &  0 \\
\verb=  sponge_kappa  = &   Parameter for sponge.  Problem dependent.  &  10.d0 \\
\verb=  stop_time  = &   simulation stop time  &  -1.d0 \\
